Project 3

### 2018-11-15 Project4/report/ms.tex
Adding tex file

\section{Data}
\label{sec:data}

@@

>>>>

@@

\begin{deluxetable}{lcc}
%\tablewidth{0pt}
\tablecaption{\label{tab:results1}}
\tablecomments{Table comparing CPU-time between the forward Euler and velocity Verlet algorithms, as a function of number of iterations, for the case of Earth revolving around the Sun, time complexity seemingly increases linearly for larger number of iterations.}
\tablecolumns{3}
\tablehead{Iterations  & Euler & Verlet}
\startdata
10^{3} & 0.000572 & 0.000838 \\
10^{4} & 0.004041 & 0.006914 \\
10^{5} & 0.13305 & 0.239944 \\
10^{6} & 1.26058 & 2.39078 \\
10^{7} & 12.649 & 23.6886 \\
10^{8} & 125.378 & 236.845  \\
\enddata
\end{deluxetable}

\section{Discussion}
\label{sec:discussion}
As seen in table \ref{tab:results1} time complexity of velocity Verlet is seemingly close to double compared to time complexity of Euler. This however is consistent with the number of FLOPS used for each of the methods as our Verlet algorithm seemingly runs at close to double the amount of FLOPS compared to Euler.
